---
title: "Basic plots"
author: "Tony Fujs"
output: rmarkdown::tufte_handout
---

```{r, echo = FALSE}
load('../data/data.Rdata')
library(ggplot2)
library(scales)
library(ggthemes)
library(knitr)
opts_chunk$set(cache=TRUE, warning = FALSE, message = FALSE)
```

## Scatter plot: Population vs Stores
```{r, eval=FALSE}
ggplot(
  aes(x = XXXX, y = XXXX),
  data = summary2005) +
  geom_point()
```

```{r, echo = FALSE, fig.margin = TRUE}
ggplot(aes(x = population, y = stores), data = summary2005) + geom_point() + theme_few()
```
.   
.   
.    
.       

## Scatter Plot: Add regression line
```{r, eval=FALSE}
ggplot(
  aes(x = population, y = stores), 
  data = summary2005) +
  geom_point() +
  geom_XXXX()
```

```{r, echo = FALSE, fig.margin = TRUE}
ggplot(aes(x = population, y = stores), data = summary2005) + geom_point() + geom_smooth() + theme_few()
```    
.   
.   
.    
.       

## Bubble plot: Bubble size represents market_share
```{r, eval=FALSE}
ggplot(data = summary2005) +
geom_point(aes(
        x = population,
        y = stores,
        XXXX = market_share))
```

```{r, echo = FALSE, fig.margin = TRUE}
# Bubbles represent market_share 
ggplot(data = summary2005) + geom_point(aes(x = population, y = stores, size = market_share)) + theme_few() + theme(legend.position="none")
```
.   
.   
.     
.       
    
## Bar chart: ordered and flipped
```{r, eval=FALSE}
ggplot(
  aes(x = reorder(state, population),
      y = population),
  data = summary2005) +
  geom_bar(stat = 'identity') +
  coord_XXXX
```

```{r, echo = FALSE, fig.margin = TRUE}
# Bubbles represent market_share 
ggplot(aes(x = reorder(state, population), y = population), data = summary2005) + 
  geom_bar(stat = 'identity') + coord_flip() + theme_few()
```
.   
.   
.    
.       

## Update the code so each bar represents the total population of the US for each year
```{r, eval=FALSE}
ggplot(
aes(x = factor(year),
    y = population),
data = summary95_05) +
geom_bar(stat = 'identity',
         position = 'identity')
```

```{r, echo = FALSE, fig.margin = TRUE}
ggplot(aes(x = factor(year), y = population), data = summary95_05) +
  geom_bar(stat = 'identity', position = 'stack') + scale_y_continuous(labels = comma) + theme_few()
```
.   
.   
.    
.       

## Fix the code below to produce this plot
```{r, eval=FALSE}
ggplot(aes(x = year, y = stores), data = summary) +
  geom_line()
```

```{r, echo = FALSE, fig.margin = TRUE}
ggplot(aes(x = year, y = stores, group = state), data = summary) +
  geom_line() + theme_few()
```
.   
.   
.     
.       

## Edit code to change lines color depending on state
```{r, eval=FALSE}
ggplot(aes(x = year, y = stores, group = state), data = summary) +
  geom_line()
```

```{r, echo = FALSE, fig.margin = TRUE}
ggplot(aes(x = year, y = stores, group = state, color = state), data = summary) +
  geom_line() + theme_few() + theme(legend.position="none")
```
.   
.   
.    
.       

## Edit the code to produce the following small multiple
```{r, eval=FALSE}
ggplot(aes(x = year, y = stores, group = state, color = state), data = summary) +
  geom_line()
```

```{r, echo = FALSE, fig.margin = TRUE}
ggplot(aes(x = year, y = stores, group = state, color = state), data = summary) +
  geom_line() + facet_wrap(~state) + theme_few() + theme(legend.position="none")
```
.   
.   
.    
.       

[^tufte_latex]: https://code.google.com/p/tufte-latex/
[^books_be]: http://www.edwardtufte.com/tufte/books_be










